They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-05 paper.tex
Conclusion, and fix long url

\subsection{Running the game}
Our game can be found at
\href{https://github.com/YourFin/They-Are-Very-Smart}{github.com/yourfin/They-Are-Very-Smart},
and downloaded with a standard \texttt{git clone} command. The relevant unity
scene is then located at
\texttt{They-Are-Very-Smart/TD/TowerDefence/Assets/Scenes/Levels/Level0/Level0.unity}
Double clicking on this file on any computer with unity installed will open up
the unity editor with the context for this paper.

@@

At this time, we are currently waiting on actual results from our project, but
we hope that given a large enough population of zombies, we might see
populations of zombies evolving to counteract players' strategies. Evolution
will likely have little trouble tackling a trivial or consistent player
strategy, like consistently rebuilding the same towers in the same place and
relying heavily on a single tower type, but evolution may have trouble keeping
up with a player that consistently changes strategy over the course of the game.
Our system of softmaxing the genome speed, health, and damage could also
result in progressively larger values relative to the mutation rate, making it
hard for long-evolved values to be changed in the face of changing player
strategies.

One approach to solving this problem could be moving towards more complicated
models of selection and reproduction than our current keep \(n\) percent,
asexually reproduce the best genomes and then do a straight pass of mutation.
Moving to a system where reproductive resources are distributed according to the
Z-score (standard deviations from the mean) or similar of fitness that give more
reproductive power to individual that more drastically improve on the status quo
could allow for a system that reacts more strongly to change. Another option
could be coding part of the mutation rate in genomes to allow evolution to
determine it's own speed. The two previous approaches could even be combined for
as dynamic an evolution environment as possible.

@@

Conceptually, evolving neural nets has the massive benefit of not worrying about
how to differentiate and nicely back-propagate

individuals that jump out ahead of the population could

Discussion: talk about the lack of direction vectors being fed into the neural nets.

may also see players coming up with ways to counteract the zombies by exploiting
elements of the fitness function and construction system in ways unforeseen,
possibly by playing in such a way as to allow the zombies to optimize for
something other than killing the player's home base. Another possibility we
might expect to see is the development of swarm or anti-swarm behavior based on
the effectiveness of player defenses, as well as zombies possibly hitting minima
or maxima depending on hard-coded numbers in the game environment.

In the future, we could experiment with elements such as variable damage output
from towers and other defenses (so as to avoid the aforementioned numeric minima
and maxima), as well as coming up with ways to encourage attacking the player's
base more as time goes on; this could include ways

>>>>

\subsection{Running the game}
Our game can be found at
\href{https://github.com/YourFin/They-Are-Very-Smart}{github.com/yourfin/They-Are-Very-Smart},
and downloaded with a standard \texttt{git clone} command. The relevant unity
scene is then located at
\url{They-Are-Very-Smart/TD/TowerDefence/Assets/Scenes/Levels/Level0/Level0.unity}
Double clicking on this file on any computer with unity installed will open up
the unity editor with the context for this paper.

@@

At this time, we are waiting on actual results from our project.
We hope that given a large enough population of zombies, we might see
populations of zombies evolving to counteract players' strategies. Evolution
will likely have little trouble tackling a trivial or consistent player
strategy, like rebuilding the same towers in the same place and
relying heavily on a single tower type, but may have trouble keeping
up with a player that constantly changes strategy over the course of the game.
Our system of softmaxing the genome speed, health, and damage could also
result in progressively larger values relative to the mutation rate, making it
hard for long-evolved high speed value to be traded for damage in the face of
changing player strategies.

Zombunnies will likely evolve around quirks in the way the
game is organized. The primary example would be having health that is just above
multiples of tower damage, allowing it to sustain an additional hit with
insignificant investment in the health stat. This particular problem could be
solved by having towers deal damage with slight randomness, but there likely
exist similar problems that have not been considered.

Players, on the other hand, may also learn to optimize around our implementation
of evolution. Conceivably clever player could develop two very different
strategies ahead of time. The player would first implement the weaker strategy,
and as soon as the zombunnies have deeply rooted themselves in the local maximum
versus that strategy, the strategy could be changed to the second strategy,
leaving the zombunnies unable to easily adapt to the new strategy.

Solving these problems would probably involve moving towards more complicated
models of selection and reproduction than our current keep \(n\) percent,
asexually reproduce the best genomes and then do a straight pass of mutation.
Moving to a system where reproductive resources are distributed according to the
Z-score (standard deviations from the mean) or similar of fitness that give more
reproductive power to individual that more drastically improve on the status quo
could allow for a system that reacts more strongly to change. Another option
could be coding part of the mutation rate in genomes to allow evolution to
determine it's own speed. The two previous approaches could even be combined for
as dynamic an evolution environment as possible.

@@

Conceptually, evolving neural nets instead of using backpropagation
has the massive benefit of not worrying about how to differentiate and nicely
back-propagate the reward/fitness function to learn, which opens up the
possibility to drop in a nerual net to replace any function in a learning
environment; on a larger timescale, the selection tournament process itself
could modeled with a recurrent neural network, and evolved over multiple plays
of the game.

Allowing the zombunnies to keep track of what they learn from game to game could
be useful as a ``hard mode'' should the base game be too easy, perhaps with the
additional information passed to the navigation function of the round. In an actual game
using this technology to evolve AI, this could be expanded to the entire
playerbase training a single pathfinding algorithm that is then redistributed to
each client, and perhaps even takes in all previous player game history as
additional input. The missing backpropagation requirement opens up
any function to becoming an neural net, and with any input.
